---
title: "Encapsulation"
drake_cache: ".chartTaiwanMap"
output: html_document
---


```{r setup, include=FALSE, drake=F}
knitr::opts_chunk$set(echo = TRUE, eval=F)
library(drake)
library(econDV)
library(dplyr)

```

## makecondition

```{r makecondition}
library(dplyr)
library(tidyr)
library(stringr)
library(googledrive)
library(readr)
library(ggplot2)
library(econDV)
econDV::setup_chinese(need2Knit = F)
rprojroot::is_rstudio_project -> .pj
.pj$make_fix_file() -> .root

imageFolder <- file.path(.root(),"img")
dataFolder <- file.path(.root(),"data")

if(!dir.exists(imageFolder)) dir.create(imageFolder)
if(!dir.exists(dataFolder)) dir.create(dataFolder)
```

## Programming for Workflow

### Initiate

  data -> graph 

```{r}
data$graph()
```
  
  ->> simplify
  
```{r}
data$simplify()
```

  ->> crop 
  
```{r}
data$crop()
```

***

This means
```{r}
data <- list(
  graph=function(){},
  simplify=function(){},
  crop=function(){}
)
```

### Morphism

Once `data$fun()`, 
```{r}
data <- list(
  graph=function(){},
  simplify=function(){},
  crop=function(){},
  restore=function(){}
)
```


## Environment

```{r}
data <- new.env(parent=.GlobalEnv) 
rlang::with_env(
    data,
    {
      graph=function(){}
      simplify=function(){}
      crop=function(){}
    }
)
```

```{r}
data <- new.env(parent=.GlobalEnv) 
rlang::with_env(
    data,
    {
      graph=function(){}
      simplify=function(){
        data$restore <- function(){}
      }
      crop=function(){
        data$restore <- function(){}
      }
    }
)
```

```{r}
data$crop()
data$simplify() # morphism
```

### Function environment

`graph/simplify/crop` have the same function environment, which means:

> When function body in execution miss something, it will look for its existence in the function environment (which is data herer).

```{r}
data <- new.env(parent=.GlobalEnv) 
rlang::with_env(
    data,
    {
      .execution_data
      graph=function(){
        data$.execution_data->
      }
      simplify=function(){
        data$.execution_data ->
        data$.backup_data <-
        data$restore <- function(){
          data$.execution_data <-
            data$.backup_data
        }
      }
      crop=function(){
        data$restore <- function(){
          data$.execution_data <-
            data$.backup_data
        }
      }
    }
)
```

  
### Simple Feature application

```{r}
dataSource <- "/Users/martinl/Dropbox/github-data/109-1-econDV/直轄市、縣市界線(TWD97經緯度)SHP格式/COUNTY_MOI_1090820.shp"

shp <- list()
require(dplyr)
require(ggplot2)
Data <- new.env(parent=.GlobalEnv) 
Data$.execution_data <-
  sf::st_read(dataSource)
rlang::with_env(
    Data,
    {
      graph=function(){
        Data$.execution_data %>%
          ggplot()+geom_sf()
      }
      simplify=function(){
        Data$.backup_data <-
          Data$.execution_data
        Data$.execution_data %>%
          rmapshaper::ms_simplify() ->
          Data$.execution_data
        
        Data$restore <- function(){
          Data$.execution_data <-
            Data$.backup_data
        }
      }
      crop=function(xmin, xmax, ymin, ymax){
        y <- 
          setNames(c(xmin, xmax, ymin, ymax), 
                   c("xmin", "xmax", "ymin", "ymax"))
        Data$.backup_data <-
          Data$.execution_data
        Data$.execution_data %>%
          sf::st_crop(
            y
          ) ->
          Data$.execution_data
         Data$restore <- function(){
          Data$.execution_data <-
            Data$.backup_data
        }
      }
    }
)
shp$data <- Data
```

```{r}
shp$data$graph() # take too much time
```

```{r}
shp$data$simplify()
shp$data$graph() # much faster
```


```{r}
# debug(shp$data$crop)
shp$data$crop(
  xmin=120, xmax=123,
  ymin=22, ymax=26
)
shp$data$graph()
```
### Function environment revisit

```{r}
environment(shp$data$restore)
```
```{r}
shp$data
```
They are different, meaning restore function in execution will not see `data$.execution_data/.backup_data`.

```{r}
shp <- list()
require(dplyr)
require(ggplot2)
Data <- new.env(parent=.GlobalEnv) 
Data$.execution_data <-
  sf::st_read(dataSource)
rlang::with_env(
    Data,
    {
      graph=function(){
        Data$.execution_data %>%
          ggplot()+geom_sf()
      }
      simplify=function(){
        Data$.backup_data <-
          Data$.execution_data
        Data$.execution_data %>%
          rmapshaper::ms_simplify() ->
          Data$.execution_data
        
        Data$restore <- restore
      }
      crop=function(xmin, xmax, ymin, ymax){
        y <- 
          setNames(c(xmin, xmax, ymin, ymax), 
                   c("xmin", "xmax", "ymin", "ymax"))
        Data$.backup_data <-
          Data$.execution_data
        Data$.execution_data %>%
          sf::st_crop(
            y
          ) ->
          Data$.execution_data
         Data$restore <- restore
      }
      
      ### helpers with Data as its function environment
      restore <- function(){
        Data$.execution_data <- Data$.backup_data
      }
    }
)
shp$data <- Data
```


```{r}
shp$data$simplify()
shp$data$crop(
  xmin=120, xmax=123,
  ymin=22, ymax=26
)
shp$data$graph()
```


```{r}
environment(shp$data$restore)
```
```{r}
shp$data
```

```{r}
shp$data$restore()
shp$data$graph()
```

## Exercise

Make the following method work:
```{r}
shp$data$export() -> finalData
```
so that finalData will be the `$.execution_data` object value.

Then design a function called **SHP**:

Input argument:

  * dataSource
  
Return: an **shp** instance that works out like our previous demonstration.

```{r SHP}
SHP <- function(dataSource) {
  shp <- list()
  require(dplyr)
  require(ggplot2)
  Data <- new.env(parent = .GlobalEnv)
  Data$.execution_data <-
    sf::st_read(dataSource)
  rlang::with_env(
    Data,
    {
      graph <- function() {
        Data$.execution_data %>%
          ggplot() +
          geom_sf()
      }
      simplify <- function() {
        Data$.backup_data <-
          Data$.execution_data
        Data$.execution_data %>%
          rmapshaper::ms_simplify() ->
        Data$.execution_data

        Data$restore <- restore
      }
      crop <- function(xmin, xmax, ymin, ymax) {
        y <-
          setNames(
            c(xmin, xmax, ymin, ymax),
            c("xmin", "xmax", "ymin", "ymax")
          )
        Data$.backup_data <-
          Data$.execution_data
        Data$.execution_data %>%
          sf::st_crop(
            y
          ) ->
        Data$.execution_data
        Data$restore <- restore
      }

      ### helpers with Data as its function environment
      restore <- function() {
        Data$.execution_data <- Data$.backup_data
      }
    }
  )
  shp$data <- Data
  return(shp)
}
```

```{r}
dataSource <- "/Users/martinl/Dropbox/github-data/109-1-econDV/直轄市、縣市界線(TWD97經緯度)SHP格式/COUNTY_MOI_1090820.shp"
shp <- SHP(dataSource)

shp$data$simplify()
shp$data$crop(
  xmin=120, xmax=123,
  ymin=22, ymax=26
)
shp$data$graph()
```

```{r}
shp$data$restore()
shp$data$graph()
```

## Simplified Version

```{r SHP}
SHP <- function(dataSource) {
  shp <- list()
  require(dplyr)
  require(ggplot2)
  Data <- new.env(parent = .GlobalEnv)
  Data$.execution_data <-
    sf::st_read(dataSource)
  rlang::with_env(
    Data,
    {
      graph <- function() {
        .execution_data %>%
          ggplot() +
          geom_sf()
      }
      simplify <- function() {
        Data$.backup_data <-
          .execution_data
        
        .execution_data %>%
          rmapshaper::ms_simplify() ->
        Data$.execution_data

        Data$restore <- restore
      }
      crop <- function(xmin, xmax, ymin, ymax) {
        y <-
          setNames(
            c(xmin, xmax, ymin, ymax),
            c("xmin", "xmax", "ymin", "ymax")
          )
        Data$.backup_data <-
          .execution_data
        .execution_data %>%
          sf::st_crop(
            y
          ) ->
        Data$.execution_data
        Data$restore <- restore
      }

      ### helpers with Data as its function environment
      restore <- function() {
        Data$.execution_data <- .backup_data
      }
    }
  )
  shp$data <- Data
  return(shp)
}
```


```{r}
library(sf)
sf::st_read("/Users/martinl/Dropbox/github-data/109-1-econDV/直轄市、縣市界線(TWD97經緯度)SHP格式/COUNTY_MOI_1090820.shp") -> taiwanMap
taiwanMap %>%
  rmapshaper::ms_simplify() -> sf_taiwan_simplify
sf_taiwan_simplify %>%
  st_crop(
    c(xmin=119, xmax=123,
    ymin=21, ymax=26)
  ) %>%
  ggplot()+geom_sf()
```
