---
title: "my research paper"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
## rmarkdown knit, produce correct Chinese characters
knitr::opts_chunk$set(fig.showtext=TRUE, fig.retina = 1)
## makecondition
library(readr)
library(ggplot2)
library(drake)
library(rmd2drake)
library(dplyr)
library(stringr)
library(showtext)
# font_add_google("Noto Sans TC")
font_add("Noto Sans TC", # 把字形加到R系統裡，取名為notoSansTC family
         regular="NotoSansTC-Regular.otf", # family裡的regular字體檔名
         bold="NotoSansTC-Bold.otf") #
showtext_auto()
theme(
  text=element_text(family = "Noto Sans TC")
  ) %>%
  theme_set()

rprojroot::is_rstudio_project -> pj
pj$make_fix_file() -> root

## 產生可讀取drake_cache的loaddd函數
source("plan_drake_myResearchPaper.R")
loaddd <- load_plan_drake_myResearchPaper
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
loaddd(ggline2Y3Y) 
ggline2Y3Y
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
loaddd(ggTwbInterestRates_bw)
ggTwbInterestRates_bw
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
